---
title: "Lab 00 - Hello IDS!"
author: "Duncan Jones"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Duncan Jones", "Matteo smirne", "Barney", 
           "Euan", "Romi", "karan"),
  github_username = c("Djones2334", "MatteoSmirne", "bmccreery", 
                      "euanriach", "romikaushik", "karan-so6"), 
  colour = c("green", "blue", "green", 
             "blue", "green", "purple"),
  hobby = c("mma", "Formula 1", "Motorsport", 
            "football", "swimming", "badminton"),
  favourite_number = c(1, 9, 4, 7, 9, 3)
)

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

# It displays the favourite number between 1 and 10 of each team member on a bar graph filled with our favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number",
          title = "Team members favourites")
```

#

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
